Lineage Analysis of CRISPR and shRNA Screens

### 2018-10-05 lineages_18Q3.Rmd
updated manuscript figures

```{r, eval=FALSE}
cn <- read.delim("./data_munging/public_18Q3_gene_cn.csv.gz", sep = ",", check.names = FALSE, header = TRUE)

@@

```{r fig.height=12, fig.width=12}
crispr_pca_data <- merge(ccl_converter[, c("Broad_ID", "group_general_lineage_name")], crispr, by = "Broad_ID")
crispr_lin <- crispr_pca_data[, 2]
crispr_pca <- prcomp(data.matrix(crispr_pca_data[, 3:ncol(crispr_pca_data)]), scale. = TRUE, center = TRUE)
plot(crispr_pca, type = "l")
biplot(crispr_pca, obs.scale = 1, var.scale = 1, groups = crispr_lin, ellipse = TRUE, circle = TRUE, )
ggord(crispr_pca, crispr_pca_data$group_general_lineage_name)
```

@@

# Gene expression (RPKM)
ge_filt <- filter(ge_melt, Hugo_Symbol %in% unique(crispr_data$Hugo_Symbol))
crispr_data <- merge(crispr_data, ge_filt, by = c("Hugo_Symbol", "Broad_ID", "CCLE_Name"), all.x = TRUE)
crispr_data$RPKM_log2 <- log2(crispr_data$RPKM + 0.0001)

@@

crispr_ptmuts_lvlA_filt_plot_faceted_truncated <- ggplot(data = crispr_ptmuts_lvlA_filt, aes(x = Mutation_Status_Nonsilent, y = Score)) +
  facet_wrap(~ Hugo_Symbol, drop = FALSE, ncol = length(unique(genes_lvlA_filt))) +
  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
  coord_cartesian(ylim = c(-2, 2)) +
  geom_boxplot(aes(fill = Mutation_Status_Nonsilent), position = position_dodge(0.85)) +
  scale_fill_manual(values = crispr_ptmuts_lvlA_filt_color) +
  geom_text(data = label_text, mapping = aes(x = 1.5, y = 2, label = p.signif.adj)) +
  guides(color = FALSE) +
  theme(legend.direction = "horizontal", legend.justification = c(0.5, 0), legend.position = c(0.5, 0), legend.box.margin = margin(c(10, 10, 10, 10)), axis.ticks.x = element_blank(), axis.text.x = element_blank(), axis.title.x = element_blank()) +
  labs(fill = "Mutation Status", y = "CERES Score", x = "Mutation Status")
crispr_ptmuts_lvlA_filt_plot_faceted_truncated
# ggsave("./plots_18Q3/manuscript/crispr_ptmuts_lvlA_filt_plot_faceted_truncated.png", crispr_ptmuts_lvlA_filt_plot_faceted_truncated, device = "png", width = 20, height = 4, units = "in")
```

@@

>>>>

```{r, eval=FALSE}
cn <- read.delim("./data_munging/public_18Q3_gene_cn_v2.csv.gz", sep = ",", check.names = FALSE, header = TRUE)

@@

```{r fig.height=12, fig.width=12}
crispr_pca_data <- merge(ccl_converter[, c("Broad_ID", "group_general_lineage_name")], crispr, by = "Broad_ID")
crispr_lin <- crispr_pca_data[, 2]
crispr_pca <- prcomp(data.matrix(crispr_pca_data[, 3:ncol(crispr_pca_data)]), scale. = TRUE, center = TRUE)
plot(crispr_pca, type = "l")
biplot(crispr_pca, obs.scale = 1, var.scale = 1, groups = crispr_lin, ellipse = TRUE, circle = TRUE)
ggord(crispr_pca, crispr_pca_data$group_general_lineage_name)
```

@@

# Gene expression (RPKM)
ge_filt <- filter(ge_melt, Hugo_Symbol %in% unique(crispr_data$Hugo_Symbol) & Broad_ID %in% unique(crispr_data$Broad_ID))
crispr_data <- merge(crispr_data, ge_filt, by = c("Hugo_Symbol", "Broad_ID", "CCLE_Name"), all.x = TRUE)
crispr_data$RPKM_log2 <- log2(crispr_data$RPKM + 0.0001)

@@

crispr_ptmuts_lvlA_filt_plot_faceted_truncated <- ggplot(data = crispr_ptmuts_lvlA_filt, aes(x = Mutation_Status_Nonsilent, y = Score)) +
  facet_wrap(~ Hugo_Symbol, drop = FALSE, ncol = length(unique(genes_lvlA_filt))) +
  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
  coord_cartesian(ylim = c(-2.5, 2.5)) +
  geom_boxplot(aes(fill = Mutation_Status_Nonsilent), position = position_dodge(0.85)) +
  scale_fill_manual(values = crispr_ptmuts_lvlA_filt_color) +
  geom_text(data = label_text, mapping = aes(x = 1.5, y = 2.5, label = p.signif.adj)) +
  guides(color = FALSE) +
  theme(legend.direction = "horizontal", legend.justification = c(0.5, 0), legend.position = c(0.5, 0), legend.box.margin = margin(c(10, 10, 10, 10)), axis.ticks.x = element_blank(), axis.text.x = element_blank(), axis.title.x = element_blank()) +
  labs(fill = "Mutation Status", y = "CERES Score", x = "Mutation Status")
crispr_ptmuts_lvlA_filt_plot_faceted_truncated
# ggsave("./plots_18Q3/manuscript/crispr_ptmuts_lvlA_filt_plot_faceted_truncated.png", crispr_ptmuts_lvlA_filt_plot_faceted_truncated, device = "png", width = 20, height = 4, units = "in")
```

@@

```{r}
lvlA_signif_summ <- lvlA_signif %>% group_by(Hugo_Symbol, group_general_lineage_name, Mutation_Status_Nonsilent) %>% tally()

# write.table(lvlA_signif_summ, file = "~/Desktop/lvlA_signif_summ_20181005.tsv", quote = FALSE, sep = "\t")
```
